\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Gesture Mouse}
\author{Ruturaj Mohite}
\date{}

\usepackage{hyperref}
\begin{document}

\maketitle

\section{Introduction}
The Python project is based on computer vision to detect
hand and it’s gestures to control mouse input.
The project uses OpenCV and Pynput as primary python
libraries to work.

\section{Problem Description}
The idea was just out of pure laziness. It is sometimes a
pain to get up from a comfy position in the bed just to skip
a YouTube ad. There should be an easy way to skip the ad,
or even click on a different video from the comfort of the
bed without having to get up.

\section{Solution}
This script provides a simple solution to the problem by
using hand gestures to control the mouse. It uses a HAAR
Cascade Classifier created by training the program against
thousands of images to detect the required gestures. Further,
the change in the detected coordinates between two
consecutive frames is used to move the mouse on the screen
using Pynput library. All the user has to do is move their
hand with their fist clenched to move the mouse and
opening the fist will result in a left mouse click.

\section{Installation}
Install all the dependencies from requirements.txt.
The requirements.txt is a vague file as of now and ‘pip
install -r requirements.txt’ won’t work. Make sure to
manually install all dependencies.
‘python3 main.py’ to run.

\section{Progress}
The project is in full working condition. However, the
 HAAR Cascade Classifier made(located as./training\_data/negs/data/cascade.xml)
needs more training.
Initially I had used about 500 images for the training which
did not work out at all. Increasing it gradually, the current
training stands at about 7000 generated(using OpenCV dev-
tools) positive images at 10 stages. The current dataset
detects consistently but with some error. For the time being,
to present the working of the project, a pre-trained HAAR
Classifier has been included in the project. I plan to use
more images and a refined dataset for the same in the near
future.
The stability of the mouse, although not terrible, is
something I would be working on to improve too.
\section{Conclusions}
\begin{description}
\item[$\bullet$]This project helped me learn Python and the OpenCV
framework a lot(even though there’s still a lot more to
learn)

\item[$\bullet$] Definitely taught me to be patient as the training takes
several hours and there were many failed attempts.

\item[$\bullet$]Made me lazier ;)
\end{description}

\section{References}
\begin{description}
\item[$\bullet$] OpenCV Docs

\url{https://docs.opencv.org/3.4/db/d28/tutorial\_cascade\_classifier.html}

\item[$\bullet$] Basic OpenCV

\url{https://www.youtube.com/watch?v=-ZrDjwXZGxI}

\item[$\bullet$]Advanced OpenCV

\url{https://www.youtube.com/watch?v=-Mhy-5YNcG4&list=PLvVx8lH-gGeC8XmmrsG855usswhwt5Tr1}

\item[$\bullet$]HAAR Cascade

\url{https://www.youtube.com/watch?v=88HdqNDQsEk}


\end{description}

\end{document}
